Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-07-29 files/Chapter2/generalvibrationmodel.tex
chapter2

In this dissertation, the stated objectives were to compare different models for use in applications. These comparisons are made in Chapter 4 and 6. Being able to express the solutions of the models as a formal series solution, enable us to compare the different models by only considering the eigenvalues and eigenfunctions of the different models. This is explained in detail in \cite{CVV18}.

>>>>

In this dissertation, the objective is to compare different linear beam and plate models for use in applications. The first of the comparisons are in Section \ref{sec:SP06}. This section is a discussion of the article \cite{SP06} comparing a Timoshenko beam model and a three dimensional beam model to empirical results. The authors of this article use the natural frequencies (equivalently the eigenvalues) to compare the different models.\\

Chapter 6 is a discussion and extension of the article \cite{LVV09}. This article compares a Timoshenko beam model to a two-dimensional beam model. This is then extended to a comparison of a two-dimensional beam model to a three-dimensional beam model as well as a comparison of a two-dimensional plate model to a three-dimensional plate model.

These comparisons are made in Chapter 4 and 6. Being able to express the solutions of the models as a formal series solution, enable us to compare the different models by only considering the eigenvalues and eigenfunctions of the different models. This is explained in detail in \cite{CVV18}.
